Finally Tagless, Partially Evaluated

### 2008-09-12 tagless/tagless-final.tex
Explain the de Bruijn representation a bit more

Although the rest of this paper continues to represent binding
using HOAS\@, our approach is compatible with de Bruijn indices.
The accompanying source file |incope-dB.ml| implements this
alternative, starting with the |Symantics| signature and the |R|
evaluator in Figure~\ref{fig:de-Bruijn}.

>>>>

Although the rest of this paper continues to represent binding
using HOAS\@, our approach is compatible with de Bruijn indices.
The accompanying source file |incope-dB.ml| implements this
alternative, starting with the |Symantics| signature and the |R|
evaluator in Figure~\ref{fig:de-Bruijn}.
In this encoding of the object language, |vz| represents the
innermost variable, |vs vz| represents the second-to-innermost variable,
and so on.  The new type argument |'h| to |repr| tracks the type of
the environment as a nested tuple, each of whose components is a
value of type |('c,'dv) vr| representing a variable of type~|'dv|.
The evaluator~|R| interprets each object term as a function
from its environment to its value.
